Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and instrument response functions as well as functionality
to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets for example to create source catalogs. Estimator classes,
which are contained in \code{gammapy.estinators} are used to
compute higher level science products such as flux and signficance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high level interface for executing analyses
defined from configuration files. In the following sections we will
introduce all sub-packages and their functionality in more detail.

>>>>

Figure~\ref{fig:data_flow} shows an overview of the different sub-packages and
their relation to each other. The \code{gammapy.data} and \code{gammapy.irf}
sub-packages define data objects to represent DL3 data, such as
event lists and IRFs as well as functionality
to the DL3 data from disk into memory. The \code{gammapy.makers} sub-package
contains the functionality to reduce the DL3 data to binned maps.
Binned maps and datasets, which represent a collection of binned
maps are defined in the \code{gammapy.maps} and \code{gammapy.datasets}
sub-packages respectively. Parametric models, which are defined in
\code{gammapy.modeling}, are used to jointly model a combination
of datasets for example to create source catalogs. Estimator classes,
which are contained in \code{gammapy.estinators} are used to
compute higher level science products such as flux and signficance maps,
light curves or flux points. Finally there is a \code{gammapy.analysis}
sub-package which provides a high level interface for executing analyses
defined from configuration files. In the following sections we will
introduce all sub-packages and their functionality in more detail.
